---
title: "Getting Started with SYNTHESIS"
author: "Mahmood Ul Hassan"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with SYNTHESIS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

**SYNTHESIS** is a robust evidence verification system designed to protect clinical guidelines from "fragile" meta-analyses. It uses a 7-layer bias correction model backed by a "Triple-Guard" ensemble.

## Step 1: Loading Data

The core function `synthesis_audit()` expects two vectors:
- `yi`: The effect sizes (e.g., Log Odds Ratios)
- `vi`: The sampling variances (SE^2)

```{r setup}
library(SYNTHESIS)

# Create a "Fragile" dataset (Small k + Outlier)
set.seed(99)
k <- 8
yi <- rnorm(k, 0.3, 0.1)
vi <- runif(k, 0.01, 0.05)
yi[8] <- 2.5 # The Outlier
vi[8] <- 0.001 # High Precision
```

## Step 2: Running the Audit

The audit runs the 7-layer model and cross-checks it against the Triple-Guard.

```{r audit}
audit <- synthesis_audit(yi, vi)
print(audit)
```

**Interpretation:**
- **Status RED:** The system detected high divergence.
- **Fail-Safe Active:** The final estimate defaulted to the robust Anchor.

## Step 3: Visualizing the Problem

Use the master diagnostic plot to see *why* the audit failed.

```{r plot, fig.width=7, fig.height=5}
plot(audit$core, audit = audit)
```

- **Top Left:** Shows the "Forest of Methods". Note the red dot (Final Decision).
- **Top Right:** Shows the Density Landscape. The outlier is far from the consensus peak.

## Step 4: Generating a Report

To share these findings, generate a standalone report.

```{r report, eval=FALSE}
synthesis_report(audit, file = "My_Audit.md")
```

## Conclusion

SYNTHESIS doesn't just pool numbers; it *interrogates* them. Use it to ensure your clinical recommendations are built on solid ground.
